---
title: "Select Gompertz parameters"
author: "Marios Christoforides s3361063"
date: "2023-09-19"
output: html_document
---

```{r}
library(lubridate)
library(plotrix)
library(stats4)
library(splines)
library(unifed)

###################################################
#COHORT LIFETABLES (updated in nov. 2016 from CBS)#
###################################################

#EN#

#MenLT<-read.table("cohort lifetable males prognostic.csv",sep=";",header=T)
MenLT = read.csv("CBS prognostische sterftekansen mannen 0-99 jaar (opgevraagd mei 2022).csv", sep = ";")
#View(MenLT)

haz.men<-MenLT[,-1]
haz.men<-rbind(0,haz.men)
#View(haz.men)
# haz.men = as.numeric(unlist(haz.men))
# haz.men = as.data.frame(haz.men)
haz.men[haz.men == "."] <- NA
rownames(haz.men)<-c(0,0.1,seq(1,99,1))
colnames(haz.men)<-seq(1850,2070,1)  ## column 0 after 2016

#WOMEN#
WomenLT = read.csv("CBS prognostische sterftekansen vrouwen 0-99 jaar (opgevraagd mei 2022).csv", sep = ";")
#View(WomenLT)

haz.women<-WomenLT[,-1]
haz.women<-rbind(0,haz.women)
haz.women[haz.women == "."] <- NA
#View(haz.women)
# haz.women = as.numeric(unlist(haz.women))
# haz.women = as.data.frame(haz.women)

rownames(haz.women)<-c(0,0.1,seq(1,99,1))
colnames(haz.women)<-seq(1850,2070,1)   ## Columns 0 after 2016


################################################
#Function  for calculating conditional survival#
################################################

#age: starMting age
#sex=1 (men), sex=2 (woman)
#(we start in age+1 because at age surv=1)#
#Maximum lifetime=110

surv.cond = function(age,sex){  
  if(age>99){
    surv<-t(as.data.frame(rep(0,ncol(haz.men)))) # add row with 0
    colnames(surv)=names(haz.men)
    rownames(surv)<-110
    surv
}else{
  index<-which(abs(age-as.numeric(rownames(haz.men)))==min(abs(age-as.numeric(rownames(haz.men))))) 
  if(sex==1){
    surv<-apply(haz.men[-c(1:(index)),],2, function(x){
      exp(-c(0, cumsum(ifelse(is.na(x), 0, x))))
	  })
  }
  else if(sex==2){
    surv<-apply(haz.women[-c(1:(index)),],2, function(x)
  	{
  	  exp(-c(0, cumsum(ifelse(is.na(x), 0, x))))
    	})
  }
  
  surv<-rbind(surv,0)
  surv= as.data.frame(surv)
  colnames(surv)=names(haz.men)
  rownames(surv)<-c(rownames(haz.men)[index:length(rownames(haz.men))],110)
  surv
}
}


###################
#SURVIVAL AT BIRTH#
###################

survMen<-surv.cond(age=0,sex=1)
survMen[which(rownames(survMen)==90),]

survWomen<-surv.cond(age=0,sex=2)
survWomen[which(rownames(survWomen)==90),]


```

# Normal model

Thw following function calculates squared sum between empirical and model-based (normal) hazards, similar functions can be constructed for other parametric models, such as Gompertz. 

```{r echo=T}
library(VGAM)
gomp_sim<-function(parms,datf){
  shape<-parms[1] #shape alpha(insfluence peakness)
  rate<-parms[2] #rate beta (influence spread)
  x<-datf[,1] #a vector of ages
  y<-datf[,2] #a vector of emirical hazards
  minsom<-sum((y - dgompertz(x, shape, rate)/(1 - pgompertz(x, shape, rate)))^2)
  minsom
}

# SHAPE AND RATE VALUES SHOULD BE LOW i.e 0.01
# y = haz.men[,1]
# x = 1:101
# gomp_sim(c(0.01,0.01),cbind(x,y))



```


We keep information after the 20th year since the fitting of the model is way better and information before 20 years it is not the main point of interest.
```{r echo=T}

longlived_w<- haz.women
haz_women <- c(0,longlived_w[,1])
haz_women <- matrix(haz_women,ncol=1)
rownames(haz_women) <- c(0:101)

haz.w.NL = stepfun(x=seq(0,100),as.numeric(haz_women))


t.integral = seq(20,101, by=1)
y <- haz.w.NL(t.integral)
x <- c(20:101)
datf <- cbind(x,y)

```
Next, you find the optimal parameters c, mu and sigma so that you minimize the distance between the model-based and observed empirical hazards: 

```{r echo=T}
set.seed(1234)
longlived_w<-optim(par = c(0.01,0.01), fn=gomp_sim, datf=datf)
longlived_w

```

To visualize if the resulting fit is satistactory, you can plot the empirical and the model-based survival probability curves:
```{r echo=T}
longlived_w_empirical <- 1 - exp(-cumsum(y)) #This is the cumulative risk as given by the lifetable
plot(x, 1 - pgompertz(x,longlived_w$par[1], longlived_w$par[2]), 
     col="blue", lwd=2, ylim=c(0,1), xlab="Age", ylab="survival function", 
     type="l")
lines(x, 1-longlived_w_empirical, col="blue", lwd=2, ylim=c(0,0.1), xlab="Age", ylab="Penetrance", lty=2)
legend("topleft", c("Model-based","Empirical"), lty=c(1,2), cex=0.6, box.lty=0, col="blue")


```