---
title: "Sim_Study_Draft1"
author: "Marios Christoforides"
date: '2022-04-01'
output: pdf_document
editor_options: 
  chunk_output_type: console
---

2. SIMULATION STUDY

Evaluating Family Scores using Simulation Study

THIS RMD FILE IS DESIGNED TO BE USED WITH 'Simulation_Setup_Functions.Rmd'

Code from SimulationStudymLRC by Rodriguez Girondo

This document is used for simulation studies designed to evaluate Family Scores in different scenarios.


###Complete Data Simulation Code
```{r}
# perc: survival percentile
#Simulation name guide
#hv = high variation
#lv = low variation
#n = 500 for all
#M = 500 for all
#sigma = exp(-1) for all
###Simulation - Complete Data

source("Longevity_Score_Simulation_Setup_Functions_marios.R")
M = 500
n = c(250,250) 
sigma = 0.2
kvec = c(8,8) #large families
# kvec = c(4,4) #small families
# kvec = c(2,2) #only parents families

threshold = TH_sig_expmin1
out <- list()
sim_name = 'large_fam_500'
# sim_name = 'small_fam_500'
# sim_name = 'paretns_fam_500'


for(j in 1:M){
  ###DATA GENERATION
  set.seed(j)
  data <- as.data.frame(Percentile.data_u(n=n, kvec = kvec, sigma = sigma))
  ###SCORE CALCULATION
  #uwLRC
  uwLRC <- numeric()
  id <- numeric()
  for(i in 1:length(unique(data$id))){
    uwLRC[i] <- sum(data$id == i & data$perc >= threshold)/sum(data$id == i)
    id[i] <- i
  }
  # print(table(uwLRC))
  
  #mean family y
  emp_mean <- numeric()
  for(i in 1:length(unique(data$id))){
    emp_mean[i] <- mean(data[data$id == i,'perc']) #change var name and y_expected to emp_mean and y respectively
  }

  #### mLRC
  Y = data$perc > threshold
  X = data$id
  # par[1] = beta
  # par[2] = log(sd)
  par=c(1,1)
  mLRC_mod <- nlminb(par, dbeta.mixed, Y=Y, X=X, control=list(trace=TRUE)) 
  est = mLRC_mod$par
  mLRC = sapply(1:length(unique(X)), function(i)
  {predict.fam(est, unique(X)[i], nsamples=2000)})

  # this is used for shorter function. Remove to run the full function  

  #first col: optimized likelihood 
  #2nd col: optimized beta 
  #3rd col: optimized log(sd)

#### Beta agnostic scores 
  #Beta_ag
  
  data$LEFTCENSOR <- rep(0, nrow(data)) #1 if death observed below threshold.
                                        #Beta_ag has no threshold so all = 0
  data$perc[which(data$perc == 0)] <- 0.001 #reclassify zeros
  data$perc[which(data$perc == 1)] <- 0.999 #reclassify ones
  
  Y <- data$perc #survival percentile
  Z <- data$id #family id
  B <- as.logical(data$LEFTCENSOR)
  Death <- as.logical(rep(1,nrow(data))) #death indicator

  estimates_ag = betareg.mixed(Y=Y, Death=Death, Z=Z, B=B) #estimate model parameters
  print(estimates_ag)

  Beta_ag = sapply(unique(Z), function(q) #calculate Beta Ag scores
  {
   Yclus = Y[Z==q]
   Deathclus = Death[Z==q]
   Bclus = B[Z==q]
    as.numeric(predict.ranef(estimates_ag, Yclus=Yclus, Deathclus=Deathclus, Bclus=Bclus, nsamples=5000))
  })
  
# 2nd column are values of beta 
# 3rd column are values of phi
# 4th column are values of s


# Beta threshold scores
  #Beta_TH
  data$LEFTCENSOR_TH <- rep(0, nrow(data))
  data$perc_TH <- rep(0,nrow(data)) #For observations with y < TH and death = 1, 
                              #reassign scuh that y = TH-0.01 and LEFTCENSOR = 1 
  
  for(i in 1:nrow(data)){
    if(data$perc[i] < threshold){
      data$perc_TH[i] <- threshold-0.01
      data$LEFTCENSOR_TH[i] <- 1
    }else{
      data$perc_TH[i] <- data$perc[i]
    }
  }

  data$perc_TH[which(data$perc_TH == 0)] <- 0.01  #reclassify zeros
  data$perc_TH[which(data$perc_TH == 1)] <- 0.99 #reclassify ones
  
  Y <- data$perc_TH
  Z <- data$id
  B <- as.logical(data$LEFTCENSOR_TH)
  Death <- as.logical(rep(1,nrow(data)))
  
  
  estimates_TH = betareg.mixed(Y=Y, Death=Death, Z=Z, B=B) #estimate model parameters
  
  
  Beta_TH = sapply(unique(Z), function(q) #calculate beta TH scores 
  {  
    Yclus = Y[Z==q]
    Deathclus = Death[Z==q]
    Bclus = B[Z==q] 
    as.numeric(predict.ranef(estimates_TH, Yclus=Yclus, Deathclus=Deathclus,Bclus=Bclus, nsamples=5000))
  })
# }
# 2nd column are values of beta 
# 3rd column are values of phi
# 4th column are values of s

  ##PERFORMANCE EVALUATION
  ###SCORE PREDICTIONS OF LONG-LIVED FAMILIES

  score <- data.frame(id = id, uwLRC = uwLRC, mLRC = mLRC, Beta_ag = Beta_ag, Beta_TH = Beta_TH, emp_mean = emp_mean)#Accuracy Metrics
  
  #true = get family id of top 10% lowest u
  #untrue = get family id of the rest
  
  seg <- c(0.05,0.1)#,0.15,0.2,0.25,0.3) #Performance metrics for top 5%,10%,15%,20%,25%,30%

  TP <- list()
  TN <- list()
  FP <- list()
  FN <- list()
  performance_df <- list()
  for(i in 1:length(seg)){
    
    #Extract families predicted to be in top XX% by each score.
    # If you use beta distribution decreasing should be T, otherwise F
      true <- unique(data[order(data$u, decreasing = F),'id'])[1:round(length(unique(data$id))*seg[i])]
      untrue <- unique(data[order(data$u, decreasing = F),'id']
                       )[(round(length(unique(data$id))*seg[i])+1):length(unique(data$u))]
      
      #get family id of top 10% highest mLRC
      mLRC_pred <- score[order(score$mLRC, decreasing = T),'id'][1:round(length(unique(data$id))*seg[i])]
      mLRC_nonpred <- score[order(score$mLRC, decreasing = T),'id'][(round(length(unique(data$id))*seg[i])+1):nrow(score)]
      #get family id of top 10% highest uwLRC
      uwLRC_pred <- score[order(score$uwLRC, decreasing = T),'id'][1:round(length(unique(data$id))*seg[i])]
      uwLRC_nonpred <- score[order(score$uwLRC, decreasing = T),'id'][(round(length(unique(data$id))*seg[i])+1):nrow(score)]
      #get family id of top 10% highest Beta_ag
      Beta_ag_pred <- score[order(score$Beta_ag, decreasing = T),'id'][1:round(length(unique(data$id))*seg[i])]
      Beta_ag_nonpred <- score[order(score$Beta_ag, decreasing = T),'id'][(round(length(unique(data$id))*seg[i])+1):nrow(score)]
      #get family id of top 10% highest Beta_TH
      Beta_TH_pred <- score[order(score$Beta_TH, decreasing = T),'id'][1:round(length(unique(data$id))*seg[i])]
      Beta_TH_nonpred <- score[order(score$Beta_TH, decreasing = T),'id'][(round(length(unique(data$id))*seg[i])+1):nrow(score)]
      #get family id of top 10% highest emp_mean
      emp_mean_pred <- score[order(score$emp_mean, decreasing = T),'id'][1:round(length(unique(data$id))*seg[i])]
      emp_mean_nonpred <- score[order(score$emp_mean, decreasing = T),'id'][(round(length(unique(data$id))*seg[i])+1):nrow(score)]
  }

      ###PERFORMANCE METRICS
      #True Positives
      mLRC_TP <- sum(mLRC_pred %in% true)/length(mLRC_pred)
      uwLRC_TP <- sum(uwLRC_pred %in% true)/length(uwLRC_pred)
      Beta_ag_TP <- sum(Beta_ag_pred %in% true)/length(Beta_ag_pred)
      Beta_TH_TP <- sum(Beta_TH_pred %in% true)/length(Beta_TH_pred)
      emp_mean_TP <- sum(emp_mean_pred %in% true)/length(emp_mean_pred)
      
      #True Negatives
      mLRC_TN <- sum(mLRC_nonpred %in% untrue)/length(mLRC_nonpred)
      uwLRC_TN <- sum(uwLRC_nonpred %in% untrue)/length(uwLRC_nonpred)
      Beta_ag_TN <- sum(Beta_ag_nonpred %in% untrue)/length(Beta_ag_nonpred)
      Beta_TH_TN <- sum(Beta_TH_nonpred %in% untrue)/length(Beta_TH_nonpred)
      emp_mean_TN <- sum(emp_mean_nonpred %in% untrue)/length(emp_mean_nonpred)
      
      #False Positive
      mLRC_FP <- 1-mLRC_TN
      uwLRC_FP <- 1-uwLRC_TN
      Beta_ag_FP <- 1-Beta_ag_TN
      Beta_TH_FP <- 1-Beta_TH_TN
      emp_mean_FP <- 1-emp_mean_TN
      
      #False Negative
      mLRC_FN <- 1-mLRC_TP
      uwLRC_FN <- 1-uwLRC_TP
      Beta_ag_FN <- 1-Beta_ag_TP
      Beta_TH_FN <- 1-Beta_TH_TP
      emp_mean_FN <- 1-emp_mean_TP
      
      #create lists of each metric
      TP[[i]] <- c(mLRC_TP,uwLRC_TP,Beta_ag_TP,Beta_TH_TP,emp_mean_TP)
      TN[[i]] <- c(mLRC_TN,uwLRC_TN,Beta_ag_TN,Beta_TH_TN,emp_mean_TN)
      FP[[i]] <- c(mLRC_FP,uwLRC_FP,Beta_ag_FP,Beta_TH_FP,emp_mean_FP)
      FN[[i]] <- c(mLRC_FN,uwLRC_FN,Beta_ag_FN,Beta_TH_FN,emp_mean_FN)
      performance_df[[i]] <- data.frame(TP=TP[[i]],TN=TN[[i]],FP=FP[[i]],FN=FN[[i]], row.names = c('mLRC','uwLRC','Beta_ag','Beta_TH','emp_mean'))

  #SPEARMAN (RANK-BASED) CORRELATIONS: SCORES VS TRUE
  cor_mLRC <- cor(as.matrix(score[,'mLRC']),as.matrix(unique(data[,'u'])), method = 'spearman')
  cor_uwLRC <- cor(as.matrix(score[,'uwLRC']),as.matrix(unique(data[,'u'])), method = 'spearman')
  cor_Beta_ag <- cor(as.matrix(score[,'Beta_ag']),as.matrix(unique(data[,'u'])), method = 'spearman')
  cor_Beta_TH <- cor(as.matrix(score[,'Beta_TH']),as.matrix(unique(data[,'u'])), method = 'spearman')
  cor_emp_mean <- cor(as.matrix(score[,'emp_mean']),as.matrix(unique(data[,'u'])), method = 'spearman')
  cor_spearman_true <- c("cor_mLRC"=cor_mLRC,'cor_uwLRC'=cor_uwLRC,'cor_Beta_ag'=cor_Beta_ag,
                         'cor_Beta_TH'=cor_Beta_TH, 'cor_emp_mean'=cor_emp_mean)
  
  #SPEARMAN CORRELATIONS: SCORES VS SCORES
  #let 1=mLRC, 2=uwLRC, 3=Beta_ag, 4=Beta_TH
  cor12 <- cor(score[,'mLRC'],score[,'uwLRC'], method = 'spearman')
  cor13 <- cor(as.matrix(score[,'mLRC']),as.matrix(score[,'Beta_ag']), method = 'spearman')
  cor14 <- cor(as.matrix(score[,'mLRC']),as.matrix(score[,'Beta_TH']), method = 'spearman')
  cor15 = cor(as.matrix(score[,'mLRC']),as.matrix(score[,'emp_mean']), method = 'spearman')
  cor23 <- cor(score[,'uwLRC'],score[,'Beta_ag'], method = 'spearman')
  cor24 <- cor(score[,'uwLRC'],score[,'Beta_TH'], method = 'spearman')
  cor25 = cor(as.matrix(score[,'uwLRC']),as.matrix(score[,'emp_mean']), method = 'spearman')
  cor34 <- cor(as.matrix(score[,'Beta_ag']),as.matrix(score[,'Beta_TH']), method = 'spearman')
  cor35 = cor(as.matrix(score[,'Beta_ag']),as.matrix(score[,'emp_mean']), method = 'spearman')
  cor45 = cor(as.matrix(score[,'emp_mean']),as.matrix(score[,'Beta_TH']), method = 'spearman')
  cor_spearman_scores <- c(cor12,cor13,cor14,cor15,cor23,cor24,cor25,cor34,cor35,cor45)
  
  #FINAL COMPILATION OF INFORMATION
  out[[j]] <- list(mLRC_mod, estimates_ag, estimates_TH, score, performance_df, cor_spearman_true, cor_spearman_scores)
  file <- list(out[[j]], data$u)
  save(file, file = paste0(j,sim_name,'.rData'))
  print(out[[j]])
}


###Procedure for saving simulation results

# small_fam_m500 <- out
# save(small_fam_m500, file = 'parents_fam_500.rData')#SAVE SIMULATION RESULTS

large_fam_m500 <- out
save(large_fam_m500, file = 'large_fam_500.rData')#SAVE SIMULATION RESULTS

# parents_fam_m500 <- out
# save(parents_fam_m500, file = 'parents_fam_500.rData')#SAVE SIMULATION RESULTS



 
```

## Plot for correlation betwwen scores and random effect u


## Plot for TPR

```{r}
## gompertz
#### BE CAREFUL WITH THE NAME INSIDE THE DATAFRAME!!!!!!
load("C:\\Users\\Marios\\OneDrive\\Υπολογιστής\\thesis\\Simulation_Scripts\\simulations\\small_fam_500.rData")

fam_rates = numeric()
for(i in 1:M){
  fam_rates[i] = as.data.frame(small_fam_m500[[i]][[5]][[2]][1])
  # print(fam_rates)
}
#### uwLRC
tpr_uwLRC = numeric()
for (i in 1:M) {
  tpr_uwLRC[i] = fam_rates[[i]][2]
  # print(tpr_uwLRC)
}
uwLRC_mean = mean(tpr_uwLRC)
uwLRC_sd = sd(tpr_uwLRC)

#### mLRC
tpr_mLRC = numeric()
for (i in 1:M) {
  tpr_mLRC[i] = fam_rates[[i]][1]
  # print(tpr_mLRC)
}
mLRC_mean = mean(tpr_mLRC)
mLRC_sd = sd(tpr_mLRC)

### empirical mean
tpr_emp = numeric()
for (i in 1:M) {
  tpr_emp[i] = fam_rates[[i]][5]
  # print(tpr_emp)
}
e_mean = mean(tpr_emp)
e_sd = sd(tpr_emp)

tpr_beta_ag = numeric()
for (i in 1:M) {
  tpr_beta_ag[i] = fam_rates[[i]][3]
  # print(tpr_beta_ag)
}
beta_ag_mean = mean(tpr_beta_ag)
beta_ag_sd = sd(tpr_beta_ag)

### beta threshold
tpr_betath = numeric()
for (i in 1:M) {
  tpr_betath[i] = fam_rates[[i]][4]
  # print(tpr_betathRC)
}
betath_mean = mean(tpr_betath)
betath_sd = sd(tpr_betath)

### The plots are adjusted based on the family size of the simulation ###

plot(density(tpr_uwLRC), col = "red",main = "TPR(4 members gompertz)", ylim = c(0,12), xlim = c(0.18,0.9))
lines(density(tpr_mLRC), col = "blue", main = "mLRC")
lines(density(tpr_beta_ag), col = "magenta", main = "Beta_ag")
lines(density(tpr_betath), col = "orange", main = "Beta threshold")
lines(density(tpr_emp), col = "green", main = "Emperical Mean")
points(uwLRC_mean, 6.8, col = "red", pch = 4)
points(mLRC_mean, 5.7, col = "blue", pch = 4)
points(beta_ag_mean, 7, col = "magenta", pch = 4)
points(betath_mean, 7.6, col = "orange", pch = 4)
points(e_mean, 6.9, col = "green", pch = 4)
text(uwLRC_mean, 9.5, "051", col = "red")
text(mLRC_mean, 8.5, "0.51", col = "blue")
text(beta_ag_mean, 8.6, "0.57", col = "magenta")
text(betath_mean, 8.8, "0.62", col = "orange")
text(e_mean, 7.5, "0.47", col = "green")
legend("topright", c("mLRC(μ: 0.51, σ: 0.07)", "uwLRC(μ: 0.51, σ: 0.06)", "Beta_ag(μ: 0.57, σ: 0.06)", "Beta_th(μ: 0.62, σ: 0.06)",  "emp_m(μ: 0.45, σ: 0.07)"), lty=1, cex=0.9,col=c("blue", "red", "magenta", "orange", "green"))






```


### Incomplete data Simulation Code
Ignore participants with survival percentile < 0.5 and calculate survival percentile for the rest of the censored observations
```{r}

source("C:\\Users\\Marios\\OneDrive\\Υπολογιστής\\thesis\\Simulation_Scripts\\simulations\\Longevity_Score_Simulation_Setup_Functions_marios.R")

#Simulation name guide
#hv = high variation
#lv = low variation
#n = 500 for all
#M = 500 for all
#sigma = exp(-1) for all
###Simulation - Complete Data

#Uncomment variables and specify values
M = 500
n = c(250,250)
sigma = 0.3
# kvec = c(8,8)
# kvec = c(4,4)
kvec = c(2,2)
threshold = TH_sig_expmin1
sim_name = 'simcens2'


#Majority of this code is identical to Complete Data scenario. 
#Refer to annotations in that section.
out_cens <- list()
for(j in 1:M) {
  ###DATA GENERATION
  set.seed(j)
  data <- as.data.frame(Percentile.data.cens.beta(n=n, kvec=kvec, sigma = sigma, censoring = T))
  data_lrc = as.data.frame(Percentile.data.cens(n=n, kvec=kvec, sigma = sigma, censoring = T))
  threshold <- threshold
  ###SCORE CALCULATION
  #uwLRC
  
  # data_lrc = data_lrc[!(data_lrc$d == 0 & data_lrc$perc < threshold | is.na(data_lrc$y)) ,  ]
  data_lrc = data_lrc[!(data_lrc$perc < 0.5 | is.na(data_lrc$y)) ,  ]
  
  #### print family sizes
  #### distribution of random effects data_lrc and data
  
  
  uwLRC <- numeric()
  id <- numeric()
  for(i in 1:length(unique(data_lrc$id))){
    uwLRC[i] <- sum(data_lrc$id == i & data_lrc$perc[i] >= threshold)/length(data_lrc$id == i)
    id[i] <- i
  }
  # print(uwLRC)
  
  #mean family y
  emp_mean <- numeric()
  for(i in 1:length(unique(data_lrc$id))){
    emp_mean[i] <- mean(data_lrc[data_lrc$id == unique(data_lrc$id)[i],'perc'])
  }
  print(emp_mean)

  #mLRC
  Y = data_lrc$perc > threshold
  X = data_lrc$id
  
  par=c(1,1)
  mLRC_mod <- nlminb(par, dbeta.mixed, Y=Y, X=X, control=list(trace=TRUE)) 
  est = mLRC_mod$par
  
  mLRC = sapply(1:length(unique(X)), function(i)
  {#print(i)
  predict.fam(est, unique(X)[i], nsamples=2000)})

  
  
  ###### FILL NON EXISTED FAMILY IDS WITH NA
  # create logical vector indicating missing id values
  missing_ids <- !(unique(data$id) %in% unique(data_lrc$id))
  
  # get indexes of missing id values
  missing_indexes <- which(missing_ids)
  # print(missing_indexes)
  
  # add NA values at missing indexes
  uwLRC <- append(uwLRC, rep(NA, length(missing_indexes)))
  emp_mean <- append(emp_mean, rep(NA, length(missing_indexes)))
  mLRC <- append(mLRC, rep(NA, length(missing_indexes)))
  
  # shift the existing values to make room for the NAs
  shifted_indexes <- missing_indexes + 1
  uwLRC[shifted_indexes] <- uwLRC[missing_indexes]
  emp_mean[shifted_indexes] <- emp_mean[missing_indexes]
  mLRC[shifted_indexes] <- mLRC[missing_indexes]
  
  # add NA values at missing indexes
  uwLRC[missing_indexes] <- NA
  emp_mean[missing_indexes] <- NA
  mLRC[missing_indexes] <- NA
  if(length(uwLRC) > 500){
    uwLRC = uwLRC[-length(mLRC)]
    mLRC = mLRC[-length(uwLRC)]
    emp_mean = emp_mean[-length(emp_mean)]
  }

  #Beta_ag
  data$LEFTCENSOR <- rep(0, nrow(data))
  data$perc[which(data$perc == 0)] <- 0.01 
  data$perc[which(data$perc == 1)] <- 0.99

  Y <- data$perc
  Z <- data$id
  B <- as.logical(data$LEFTCENSOR)
  Death <- data$d

  
  estimates_ag = betareg.mixed(Y=Y, Death=Death, Z=Z, B=B)

  Beta_ag = sapply(unique(Z), function(q) 
  {  
   Yclus = Y[Z==q]
   Deathclus = Death[Z==q]
   Bclus = B[Z==q] 
    as.numeric(predict.ranef(estimates_ag, Yclus=Yclus, Deathclus=Deathclus,Bclus=Bclus, nsamples=5000))
  })

  #Beta_TH
  data$LEFTCENSOR_TH <- rep(0, nrow(data))
  data$perc_TH <- rep(0,nrow(data))
  
  for(i in 1:nrow(data)){
    if(data$perc[i] < threshold){ 
      data$perc_TH[i] <- threshold-0.01
      data$LEFTCENSOR_TH[i] <- 1
    }else{
      data$perc_TH[i] = data$perc[i]
    }
    
  }
  data$perc_TH[which(data$perc_TH == 0)] <- 0.01 
  data$perc_TH[which(data$perc_TH == 1)] <- 0.99
 
  Y <- data$perc_TH
  Z <- data$id
  B <- as.logical(data$LEFTCENSOR_TH)
  Death <- data$d
  
  estimates_TH = betareg.mixed(Y=Y, Death=Death, Z=Z, B=B)
  
 
  Beta_TH = sapply(unique(Z), function(q) 
  {  
    Yclus = Y[Z==q]
    Deathclus = Death[Z==q]
    Bclus = B[Z==q] 
    as.numeric(predict.ranef(estimates_TH, Yclus=Yclus, Deathclus=Deathclus,Bclus=Bclus, nsamples=5000))
  })
 
  
  ###SCORE PREDICTIONS OF LONG-LIVED FAMILIES
  #score df
  score <- data.frame(id = unique(data$id), uwLRC = uwLRC, mLRC = mLRC, Beta_ag = Beta_ag, Beta_TH = Beta_TH, emp_mean = emp_mean)
  # View(score)
  
  data_lrc = data
  data_lrc[data$perc == 0 & data$perc < threshold, ] <- NA   
  data_lrc[data$u == 0 & data$perc < threshold, ] <- NA   
  data_lrc[data$id == 0 & data$perc < threshold, ] <- NA   
  
  #Accuracy Metrics
  #true = get family id of top 10% lowest u
  seg <- c(0.05,0.1)#,0.15,0.2,0.25,0.3)

  TP <- list()
  TN <- list()
  FP <- list()
  FN <- list()
  performance_df <- list()
  for(i in 1:length(seg)){
      true <- unique(data[order(data$u, decreasing = F),'id'])[1:round(length(unique(data$id))*seg[i])]
      untrue <- unique(data[order(data$u, decreasing = F),'id'])[(round(length(unique(data$id))*seg[i])+1):length(unique(data$u))]
      
      true_lrc <- unique(data_lrc[order(data_lrc$u, decreasing = F),'id'])[1:round(length(unique(data_lrc$id))*seg[i])]
      untrue_lrc <- unique(data_lrc[order(data_lrc$u, decreasing = F),'id'])[(round(length(unique(data_lrc$id))*seg[i])+1):length(unique(data_lrc$u))]
      
      #get family id of top 10% highest mLRC
      mLRC_pred <- score[order(score$mLRC, decreasing = T),'id'][1:round(length(unique(data_lrc$id))*seg[i])]
      mLRC_nonpred <- score[order(score$mLRC, decreasing = T),'id'][(round(length(unique(data_lrc$id))*seg[i])+1):nrow(score)]
      #get family id of top 10% highest uwLRC
      uwLRC_pred <- score[order(score$uwLRC, decreasing = T),'id'][1:round(length(unique(data_lrc$id))*seg[i])]
      uwLRC_nonpred <- score[order(score$uwLRC, decreasing = T),'id'][(round(length(unique(data_lrc$id))*seg[i])+1):nrow(score)]
      #get family id of top 10% highest Beta_ag
      Beta_ag_pred <- score[order(score$Beta_ag, decreasing = T),'id'][1:round(length(unique(data$id))*seg[i])]
      Beta_ag_nonpred <- score[order(score$Beta_ag, decreasing = T),'id'][(round(length(unique(data$id))*seg[i])+1):nrow(score)]
      #get family id of top 10% highest Beta_TH
      Beta_TH_pred <- score[order(score$Beta_TH, decreasing = T),'id'][1:round(length(unique(data$id))*seg[i])]
      Beta_TH_nonpred <- score[order(score$Beta_TH, decreasing = T),'id'][(round(length(unique(data$id))*seg[i])+1):nrow(score)]
      #get family id of top 10% highest emp_mean
      emp_mean_pred <- score[order(score$emp_mean, decreasing = T),'id'][1:round(length(unique(data_lrc$id))*seg[i])]
      emp_mean_nonpred <- score[order(score$emp_mean, decreasing = T),'id'][(round(length(unique(data_lrc$id))*seg[i])+1):nrow(score)]

  
      ###PERFORMANCE METRICS
      #True Positives
      mLRC_TP <- sum(mLRC_pred %in% true_lrc)/length(mLRC_pred)
      uwLRC_TP <- sum(uwLRC_pred %in% true_lrc)/length(uwLRC_pred)
      Beta_ag_TP <- sum(Beta_ag_pred %in% true)/length(Beta_ag_pred)
      Beta_TH_TP <- sum(Beta_TH_pred %in% true)/length(Beta_TH_pred)
      emp_mean_TP <- sum(emp_mean_pred %in% true_lrc)/length(emp_mean_pred)
      #True Negatives
      mLRC_TN <- sum(mLRC_nonpred %in% untrue_lrc)/length(mLRC_nonpred)
      uwLRC_TN <- sum(uwLRC_nonpred %in% untrue_lrc)/length(uwLRC_nonpred)
      Beta_ag_TN <- sum(Beta_ag_nonpred %in% untrue)/length(Beta_ag_nonpred)
      Beta_TH_TN <- sum(Beta_TH_nonpred %in% untrue)/length(Beta_TH_nonpred)
      emp_mean_TN <- sum(emp_mean_nonpred %in% untrue_lrc)/length(emp_mean_nonpred)
      #False Positive
      mLRC_FP <- 1-mLRC_TN
      uwLRC_FP <- 1-uwLRC_TN
      Beta_ag_FP <- 1-Beta_ag_TN
      Beta_TH_FP <- 1-Beta_TH_TN
      emp_mean_FP <- 1 - emp_mean_TN
      #False Negative
      mLRC_FN <- 1-mLRC_TP
      uwLRC_FN <- 1-uwLRC_TP
      Beta_ag_FN <- 1-Beta_ag_TP
      Beta_TH_FN <- 1-Beta_TH_TP
      emp_mean_FN <- 1-emp_mean_TP
      
      TP[[i]] <- c(mLRC_TP,uwLRC_TP,Beta_ag_TP,Beta_TH_TP, emp_mean_TP)
      TN[[i]] <- c(mLRC_TN,uwLRC_TN,Beta_ag_TN,Beta_TH_TN, emp_mean_TN)
      FP[[i]] <- c(mLRC_FP,uwLRC_FP,Beta_ag_FP,Beta_TH_FP, emp_mean_FP)
      FN[[i]] <- c(mLRC_FN,uwLRC_FN,Beta_ag_FN,Beta_TH_FN, emp_mean_FN)
      performance_df[[i]] <- data.frame(TP=TP[[i]],TN=TN[[i]],FP=FP[[i]],FN=FN[[i]], row.names = c('mLRC','uwLRC','Beta_ag','Beta_TH', 'emp_mean'))
  }
  
  #SPEARMAN (RANK-BASED) CORRELATIONS: SCORES VS TRUE
  
  cor_mLRC <- cor(score[,'mLRC'],unique(data_lrc[,'u']), method = 'spearman', use="pairwise.complete.obs")
  cor_uwLRC <- cor(score[,'uwLRC'],unique(data_lrc[,'u']), method = 'spearman', use="pairwise.complete.obs")
  cor_Beta_ag <- cor(score[,'Beta_ag'],unique(data[,'u']), method = 'spearman', use="pairwise.complete.obs")
  cor_Beta_TH <- cor(score[,'Beta_TH'],unique(data[,'u']), method = 'spearman', use="pairwise.complete.obs")
  cor_emp_mean <- cor(score[,'emp_mean'],unique(data_lrc[,'u']), method = 'spearman', use="pairwise.complete.obs")
  

  # add NA values at missing indexes
  # cor_mLRC[missing_indexes] <- NA
  # cor_emp_mean[missing_indexes] <- NA
  # cor_uwLRC[missing_indexes] <- NA
  
  cor_spearman_true <- c("cor_mLRC"=cor_mLRC, 'cor_uwLRC'=cor_uwLRC,'cor_Beta_ag'=cor_Beta_ag,'cor_Beta_TH'=cor_Beta_TH,
                         'cor_emp_mean'= cor_emp_mean)

  #SPEARMAN CORRELATIONS: SCORES VS SCORES
  #let 1=mLRC, 2=uwLRC, 3=Beta_ag, 4=Beta_TH
  cor12 <- cor(score[,'mLRC'],score[,'uwLRC'], method = 'spearman', use="pairwise.complete.obs")
  cor13 <- cor(score[,'mLRC'],score[,'Beta_ag'], method = 'spearman', use="pairwise.complete.obs")
  cor14 <- cor(score[,'mLRC'],score[,'Beta_TH'], method = 'spearman', use="pairwise.complete.obs")
  cor23 <- cor(score[,'uwLRC'],score[,'Beta_ag'], method = 'spearman', use="pairwise.complete.obs")
  cor24 <- cor(score[,'uwLRC'],score[,'Beta_TH'], method = 'spearman', use="pairwise.complete.obs")
  cor34 <- cor(score[,'Beta_ag'],score[,'Beta_TH'], method = 'spearman', use="pairwise.complete.obs")
  cor_spearman_scores <- c(cor12,cor13,cor14,cor23,cor24,cor34)

  
  #FINAL COMPILATION OF INFORMATION
  out_cens[[j]] <- list(mLRC_mod,estimates_ag,estimates_TH,score, performance_df, cor_spearman_true, cor_spearman_scores)
  file <- out_cens[[j]]
  save(file, file = paste0(j,sim_name,'.rData'))
  print(out_cens[[j]])
}


sim_cens2 <- out_cens #RENAME OUT WITH PARAMETERS
save(sim_cens2, file = 'simcens2.rData') #SAVE SIMULATION RESULTS




```

```{r}
### TPR
## gompertz
#### BE CAREFUL WITH THE NAME INSIDE THE DATAFRAME!!!!!!
library(dplyr)
load("C:\\Users\\Marios\\OneDrive\\Υπολογιστής\\thesis\\Simulation_Scripts\\simulations\\simcens8.rData")
fam_rates = numeric()
for (i in 1:M){
  fam_rates[i] = as.data.frame(sim_cens8[[i]][[5]][[2]][1])
  # print(fam_rates)
}
#### mLRC
tpr_mLRC = numeric()
for (i in 1:M) {
  tpr_mLRC[i] = fam_rates[[i]][1]
  # print(tpr_mLRC)
}
mLRC_mean = mean(tpr_mLRC)
mLRC_sd = sd(tpr_mLRC)

#### uwLRC
tpr_uwLRC = numeric()
for (i in 1:M) {
  tpr_uwLRC[i] = fam_rates[[i]][2]
  # print(tpr_uwLRC)
}
uwLRC_mean = mean(tpr_uwLRC)
uwLRC_sd = sd(tpr_uwLRC)
#### beta ag
tpr_beta_ag = numeric()
for (i in 1:M) {
  tpr_beta_ag[i] = fam_rates[[i]][3]
  # print(tpr_beta_ag)
}
beta_ag_mean = mean(tpr_beta_ag)
beta_ag_sd = sd(tpr_beta_ag)

#### beta threshold
tpr_betath = numeric()
for (i in 1:M) {
  tpr_betath[i] = fam_rates[[i]][4]
  # print(tpr_betath)
}
betath_mean = mean(tpr_betath)
betath_sd = sd(tpr_betath)

#### empirical mean
tpr_emp = numeric()
for (i in 1:M) {
  tpr_emp[i] = fam_rates[[i]][5]
  # print(tpr_emp)
}
e_mean = mean(tpr_emp)
e_sd = sd(tpr_emp)

### The plots are adjusted based on the family size of the simulation ###

plot(density(tpr_uwLRC), col = "red",main = "TPR(8 members excluding percentiles < 0.5)", ylim = c(0,18), xlim = c(0,0.5))
lines(density(tpr_mLRC), col = "blue", main = "mLRC")
lines(density(tpr_beta_ag), col = "magenta", main = "Beta_ag")
lines(density(tpr_betath), col = "orange", main = "Beta threshold")
lines(density(tpr_emp), col = "green", main = "Emperical Mean")
points(uwLRC_mean, 9.1, col = "red", pch = 4)
points(mLRC_mean, 8.7, col = "blue", pch = 4)
points(beta_ag_mean, 6.5, col = "magenta", pch = 4)
points(betath_mean, 8.7, col = "orange", pch = 4)
points(e_mean, 11.3, col = "green", pch = 4)
text(uwLRC_mean, 12.5, "0.10", col = "red")
text(mLRC_mean, 14, "0.10", col = "blue")
text(beta_ag_mean, 8.1, "0.33", col = "magenta")
text(betath_mean, 9.9, "0.27", col = "orange")
text(e_mean, 16, "0.10", col = "green")
legend("topright", c("mLRC(μ: 0.10, σ: 0.04)", "uwLRC(μ: 0.10, σ: 0.04)", "Beta_ag(μ: 0.33, σ: 0.06)", "Beta_th(μ: 0.27, σ: 0.06)",  "emp_m(μ: 0.10, σ: 0.05)"), lty=1, cex=1,col=c("blue", "red", "magenta", "orange", "green"))


```



## Incomplete data
Calculate the expected percentile for every observation

```{r}
source("C:\\Users\\Marios\\OneDrive\\Υπολογιστής\\thesis\\Simulation_Scripts\\simulations\\Longevity_Score_Simulation_Setup_Functions_marios.R")

M = 500
n = c(250,250)
sigma = 0.3
# kvec = c(8,8)
# kvec = c(4,4)
kvec = c(2,2)
threshold = TH_sig_expmin1
sim_name = 'simcensexp2'

out <- list()
for(j in 1:M) {
  ###DATA GENERATION
  set.seed(j)
  data <- as.data.frame(Percentile.data.cens.beta(n=n, kvec=kvec, sigma = sigma, censoring = T))
  data_lrc = as.data.frame(Percentile.data.cens(n=n, kvec=kvec, sigma = sigma, censoring = T))
  threshold <- threshold
  ###SCORE CALCULATION

  #uwLRC
  uwLRC <- numeric()
  id <- numeric()
  for(i in 1:length(unique(data$id))){
    uwLRC[i] <- sum(data$id == i & data$perc[i] >= threshold)/length(data$id == i)
    id[i] <- i
  }
  # print(uwLRC)
  
  #mean family y
  emp_mean <- numeric()
  for(i in 1:length(unique(data$id))){
    emp_mean[i] <- mean(data_lrc[data$id == unique(data$id)[i],'perc'])
  }
  # print(emp_mean)
  
  #mLRC
  Y = data$perc > threshold
  X = data$id
  
  par=c(1,1)
  mLRC_mod <- nlminb(par, dbeta.mixed, Y=Y, X=X, control=list(trace=TRUE)) 
  est = mLRC_mod$par
  
  mLRC = sapply(1:length(unique(X)), function(i)
  {#print(i)
  predict.fam(est, unique(X)[i], nsamples=2000)})
  
  #Beta_ag
  data$LEFTCENSOR <- rep(0, nrow(data))
  data$perc[which(data$perc == 0)] <- 0.01 
  data$perc[which(data$perc == 1)] <- 0.99

  Y <- data$perc
  Z <- data$id
  B <- as.logical(data$LEFTCENSOR)
  Death <- data$d

  
  estimates_ag = betareg.mixed(Y=Y, Death=Death, Z=Z, B=B)

  Beta_ag = sapply(unique(Z), function(q) 
  {  
   Yclus = Y[Z==q]
   Deathclus = Death[Z==q]
   Bclus = B[Z==q] 
    as.numeric(predict.ranef(estimates_ag, Yclus=Yclus, Deathclus=Deathclus,Bclus=Bclus, nsamples=5000))
  })

  #Beta_TH
  data$LEFTCENSOR_TH <- rep(0, nrow(data))
  data$perc_TH <- rep(0,nrow(data))
  
  for(i in 1:nrow(data)){
    if(data$perc[i] < threshold){ 
      data$perc_TH[i] <- threshold-0.01
      data$LEFTCENSOR_TH[i] <- 1
    }else{
      data$perc_TH[i] = data$perc[i]
    }
    
  }
  data$perc_TH[which(data$perc_TH == 0)] <- 0.01 
  data$perc_TH[which(data$perc_TH == 1)] <- 0.99
 
  Y <- data$perc_TH
  Z <- data$id
  B <- as.logical(data$LEFTCENSOR_TH)
  Death <- data$d
  
  estimates_TH = betareg.mixed(Y=Y, Death=Death, Z=Z, B=B)
  
 
  Beta_TH = sapply(unique(Z), function(q) 
  {  
    Yclus = Y[Z==q]
    Deathclus = Death[Z==q]
    Bclus = B[Z==q] 
    as.numeric(predict.ranef(estimates_TH, Yclus=Yclus, Deathclus=Deathclus,Bclus=Bclus, nsamples=5000))
  })
  
  ###SCORE PREDICTIONS OF LONG-LIVED FAMILIES
  #score df
  score <- data.frame(id = id, uwLRC = uwLRC, mLRC = mLRC, Beta_ag = Beta_ag, Beta_TH = Beta_TH, emp_mean = emp_mean)
  #Accuracy Metrics
  #true = get family id of top 10% lowest u
  
  u_vec <- numeric()
  for(i in 1:max(data$id)){
    id_subset <- data[data$id == i, 'u']
    u_vec[i] <- id_subset[1]
  
  }
  u_df <- cbind(u_vec,1:max(data$id))
  colnames(u_df) <- c('u','id')
  u_df <- as.data.frame(u_df)
  
  seg <- c(0.1) #Performance metrics for top 10%

  TP <- list()
  TN <- list()
  FP <- list()
  FN <- list()
  performance_df <- list()
  for(i in 1:length(seg)){
    true <- unique(data[order(data$u, decreasing = F),'id'])[1:round(length(unique(data$id))*seg[i])]
      untrue <- unique(data[order(data$u, decreasing = F),'id'])[(round(length(unique(data$id))*seg[i])+1):length(unique(data$u))]
      
      #get family id of top 10% highest mLRC
      mLRC_pred <- score[order(score$mLRC, decreasing = T),'id'][1:round(length(unique(data$id))*seg[i])]
      mLRC_nonpred <- score[order(score$mLRC, decreasing = T),'id'][(round(length(unique(data$id))*seg[i])+1):nrow(score)]
      #get family id of top 10% highest uwLRC
      uwLRC_pred <- score[order(score$uwLRC, decreasing = T),'id'][1:round(length(unique(data$id))*seg[i])]
      uwLRC_nonpred <- score[order(score$uwLRC, decreasing = T),'id'][(round(length(unique(data$id))*seg[i])+1):nrow(score)]
      #get family id of top 10% highest Beta_ag
      Beta_ag_pred <- score[order(score$Beta_ag, decreasing = T),'id'][1:round(length(unique(data$id))*seg[i])]
      Beta_ag_nonpred <- score[order(score$Beta_ag, decreasing = T),'id'][(round(length(unique(data$id))*seg[i])+1):nrow(score)]
      #get family id of top 10% highest Beta_TH
      Beta_TH_pred <- score[order(score$Beta_TH, decreasing = T),'id'][1:round(length(unique(data$id))*seg[i])]
      Beta_TH_nonpred <- score[order(score$Beta_TH, decreasing = T),'id'][(round(length(unique(data$id))*seg[i])+1):nrow(score)]
      #get family id of top 10% highest emp_mean
      emp_mean_pred <- score[order(score$emp_mean, decreasing = T),'id'][1:round(length(unique(data$id))*seg[i])]
      emp_mean_nonpred <- score[order(score$emp_mean, decreasing = T),'id'][(round(length(unique(data$id))*seg[i])+1):nrow(score)]
      
      ###PERFORMANCE METRICS
      #True Positives
      mLRC_TP <- sum(mLRC_pred %in% true)/length(mLRC_pred)
      uwLRC_TP <- sum(uwLRC_pred %in% true)/length(uwLRC_pred)
      Beta_ag_TP <- sum(Beta_ag_pred %in% true)/length(Beta_ag_pred)
      Beta_TH_TP <- sum(Beta_TH_pred %in% true)/length(Beta_TH_pred)
      emp_mean_TP <- sum(emp_mean_pred %in% true)/length(emp_mean_pred)
      #True Negatives
      mLRC_TN <- sum(mLRC_nonpred %in% untrue)/length(mLRC_nonpred)
      uwLRC_TN <- sum(uwLRC_nonpred %in% untrue)/length(uwLRC_nonpred)
      Beta_ag_TN <- sum(Beta_ag_nonpred %in% untrue)/length(Beta_ag_nonpred)
      Beta_TH_TN <- sum(Beta_TH_nonpred %in% untrue)/length(Beta_TH_nonpred)
      emp_mean_TN <- sum(emp_mean_nonpred %in% untrue)/length(emp_mean_nonpred)
      #False Positive
      mLRC_FP <- 1-mLRC_TN
      uwLRC_FP <- 1-uwLRC_TN
      Beta_ag_FP <- 1-Beta_ag_TN
      Beta_TH_FP <- 1-Beta_TH_TN
      emp_mean_FP <- 1-emp_mean_TN
      #False Negative
      mLRC_FN <- 1-mLRC_TP
      uwLRC_FN <- 1-uwLRC_TP
      Beta_ag_FN <- 1-Beta_ag_TP
      Beta_TH_FN <- 1-Beta_TH_TP
      emp_mean_FN <- 1-emp_mean_TP
      
      TP[[i]] <- c(mLRC_TP,uwLRC_TP,Beta_ag_TP,Beta_TH_TP,emp_mean_TP)
      TN[[i]] <- c(mLRC_TN,uwLRC_TN,Beta_ag_TN,Beta_TH_TN,emp_mean_TN)
      FP[[i]] <- c(mLRC_FP,uwLRC_FP,Beta_ag_FP,Beta_TH_FP,emp_mean_FP)
      FN[[i]] <- c(mLRC_FN,uwLRC_FN,Beta_ag_FN,Beta_TH_FN,emp_mean_FN)
      performance_df[[i]] <- data.frame(TP=TP[[i]],TN=TN[[i]],FP=FP[[i]],FN=FN[[i]], row.names = c('mLRC','uwLRC','Beta_ag','Beta_TH','emp_mean'))
  }

  #SPEARMAN (RANK-BASED) CORRELATIONS: SCORES VS TRUE
  cor_mLRC <- cor(score[,'mLRC'],u_df$u, method = 'spearman')
  cor_uwLRC <- cor(score[,'uwLRC'],u_df$u, method = 'spearman')
  cor_Beta_ag <- cor(score[,'Beta_ag'],u_df$u, method = 'spearman')
  cor_Beta_TH <- cor(score[,'Beta_TH'],u_df$u, method = 'spearman')
  cor_emp_mean <- cor(score[,'emp_mean'],u_df$u, method = 'spearman')
  cor_spearman_true <- c("cor_mLRC"=cor_mLRC, 'cor_uwLRC'=cor_uwLRC,'cor_Beta_ag'=cor_Beta_ag,'cor_Beta_TH'=cor_Beta_TH, 'cor_emp_mean'=cor_emp_mean)
  
  #SPEARMAN CORRELATIONS: SCORES VS SCORES
  #let 1=mLRC, 2=uwLRC, 3=Beta_ag, 4=Beta_TH
  cor12 <- cor(score[,'mLRC'],score[,'uwLRC'], method = 'spearman')
  cor13 <- cor(score[,'mLRC'],score[,'Beta_ag'], method = 'spearman')
  cor14 <- cor(score[,'mLRC'],score[,'Beta_TH'], method = 'spearman')
  cor23 <- cor(score[,'uwLRC'],score[,'Beta_ag'], method = 'spearman')
  cor24 <- cor(score[,'uwLRC'],score[,'Beta_TH'], method = 'spearman')
  cor34 <- cor(score[,'Beta_ag'],score[,'Beta_TH'], method = 'spearman')
  cor_spearman_scores <- c(cor12,cor13,cor14,cor23,cor24,cor34)
  
  
  
  #FINAL COMPILATION OF INFORMATION
  out[[j]] <- list(mLRC_mod,estimates_ag,estimates_TH,score, performance_df, cor_spearman_true, cor_spearman_scores)#,data)
  file <- out[[j]]
  save(file, file = paste0(j,sim_name,'.rdata'))  # instead name name use hv or lv
  print(out[[j]])
}
 
sim_cens_exp2 <- out #RENAME OUT WITH PARAMETERS
save(sim_cens_exp2, file = 'simcensexp2.rData') #SAVE SIMULATION RESULTS



```


```{r}
load("C:\\Users\\Marios\\OneDrive\\Υπολογιστής\\thesis\\Simulation_Scripts\\simulations\\simcensexp8.rData")

fam_rates = numeric()
for(i in 1:M){
  fam_rates[i] = as.data.frame(sim_cens_exp8[[i]][[5]][[1]][1])
  # print(fam_rates)
}

#### mLRC
tpr_mLRC = numeric()
for (i in 1:M) {
  tpr_mLRC[i] = fam_rates[[i]][1]
  # print(tpr_mLRC)
}

mLRC_mean = mean(tpr_mLRC)
mLRC_sd = sd(tpr_mLRC)


#### uwLRC
tpr_uwLRC = numeric()
for (i in 1:M) {
  tpr_uwLRC[i] = fam_rates[[i]][2]
  # print(tpr_uwLRC)
}

uwLRC_mean = mean(tpr_uwLRC)
uwLRC_sd = sd(tpr_uwLRC)


tpr_emp = numeric()
for (i in 1:M) {
  tpr_emp[i] = fam_rates[[i]][5]
  # print(tpr_emp)
}

e_mean = mean(tpr_emp)
e_sd = sd(tpr_emp)

tpr_beta_ag = numeric()
for (i in 1:M) {
  tpr_beta_ag[i] = fam_rates[[i]][3]
  # print(tpr_beta_ag)
}

beta_ag_mean = mean(tpr_beta_ag)
beta_ag_sd = sd(tpr_beta_ag)

tpr_betath = numeric()
for (i in 1:M) {
  tpr_betath[i] = fam_rates[[i]][4]
  # print(tpr_betathRC)
}

betath_mean = mean(tpr_betath)
betath_sd = sd(tpr_betath)

### The plots are adjusted based on the family size of the simulation ###

plot(density(tpr_uwLRC), col = "red",main = "TPR(8 members, censoring, full dataset)", ylim = c(0,18), xlim = c(0,0.6))
lines(density(tpr_mLRC), col = "blue", main = "mLRC")
lines(density(tpr_beta_ag), col = "magenta", main = "Beta_ag")
lines(density(tpr_betath), col = "orange", main = "Beta threshold")
lines(density(tpr_emp), col = "green", main = "Emperical Mean")
points(uwLRC_mean, 10.1, col = "red", pch = 4)
points(mLRC_mean, 8, col = "blue", pch = 4)
points(beta_ag_mean, 6.5, col = "magenta", pch = 4)
points(betath_mean, 5.9, col = "orange", pch = 4)
points(e_mean, 10.8, col = "green", pch = 4)
text(uwLRC_mean, 14, "0.10", col = "red")
text(mLRC_mean, 8.9, "0.23", col = "blue")
text(beta_ag_mean, 7.8, "0.33", col = "magenta")
text(betath_mean, 8, "0.27", col = "orange")
text(e_mean, 12.5, "0.10", col = "green")
legend("topright", c("mLRC(μ: 0.23, σ: 0.06)", "uwLRC(μ: 0.10, σ: 0.04)", "Beta_ag(μ: 0.33, σ: 0.06)", "Beta_th(μ: 0.27, σ: 0.06)",  "emp_m(μ: 0.10, σ: 0.04)"), lty=1, cex=1,col=c("blue", "red", "magenta", "orange", "green"))



```


```{r}
#### Plot density of family sizes after censoring
set.seed(123)

data <- as.data.frame(Percentile.data.cens(n=n, kvec=kvec, sigma = sigma, censoring = T))
threshold <- threshold
data_0.5 = data[!(data$d == 0 & data$perc < 0.5),  ]
l = numeric()
for(j in 1:length(unique(data_0.5$id))){
  u_ids = unique(data_0.5$id)
  # print(u_ids)
  l[j] = nrow(data_0.5[data_0.5$id == u_ids[j],])
}

plot(density(l))
hist(l,breaks = 8, col = "blue", main = "Family size percentile > 0.5", xlab = "family size")

data <- as.data.frame(Percentile.data.cens(n=n, kvec=kvec, sigma = sigma, censoring = T))
threshold <- threshold
data = data[!(data$d == 0 & data$perc < threshold),  ]
f_l = numeric()
for(j in 1:length(unique(data$id))){
  u_ids = unique(data$id)
  f_l[j] = nrow(data_lrc[data_lrc$id == u_ids[j],])
}
plot(density(f_l))
hist(l,breaks = 8, col = "blue", main = "Family sizes in Censored data", xlab = "family size")

```








